Figures

### 2025-03-08 Figures/PaperFiguresextended.Rmd
updated figure code

#Figure 2b epithelial cells
Fig2b_2 <- DimPlot(EndoAtlas_epithelial_reintegrated, reduction = "umap", group.by = "MenstrualCyclePhase", raster = FALSE)
Fig2b_2
ggsave(filename = paste0(dir_out, 'Fig2b_2.pdf'),
       plot = Fig2b_2,
       width =20, height=9)

>>>>

#Figure 2b epithelial cells
Fig2b_2 <- DimPlot(epithelial_cells_monocle3, reduction = "umap", group.by = "MenstrualCyclePhase", raster = FALSE)
Fig2b_2
ggsave(filename = paste0(dir_out, 'Fig2b_2.pdf'),
       plot = Fig2b_2,
       width =20, height=9)
